\huge Tor's Usability for Censorship Circumvention

### 2016-04-14 pets2017-paper/pets2017-paper.tex
Summary table of environments.

>>>>

\begin{figure}
\centering
\begin{tabular}{r c c c}
& E1 & E2 & E3 \\
% \noalign{\hrule}
websites blocked & X & & \\
public relays blocked & X & X & \\
default bridges blocked & X & X & X \\
\end{tabular}
\caption{
Summary of our simulated censorship environments.
E1 only requires participants to click ``Connect'';
E2 requires selection of an included bridge;
and E3 requires selection of a specific included bridge,
or manual configuration of a custom bridge.
E2's blocking is a superset of E1's;
similarly E3's is a superset of E2's.
}
\label{tab:environments}
\end{figure}
